\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://shreyasb.com/}{\Large Shreyas Bapat}} & Email : \href{mailto:contact@shreyasb.com}{b16145@students.iitmandi.ac.in}\\
  \href{https://shreyasb.com/}{https://shreyasb.com} & Mobile : +91-913-185-1172 & \href{https://github.com/shreyasbapat/}{GitHub: shreyasbapat} & \href{https://www.linkedin.com/in/shreyasbapat}{LinkedIn: shreyasbapat} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
   % \resumeSubheading
     % {Georgia Institute of Technology}{Atlanta, GA}
    %  {Master of Science in Computer Science;  GPA: 4.00}{Aug. 2012 -- Dec. 2013}
    \resumeSubheading
      {Indian Institute of Technology Mandi}{Mandi, India}
      {Bachelor of Technology in Electrical Engineering;  CGPA: 7.51/10.0}{Aug. 2016 -- Present}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Projecthiko 1.O - The Voice and Internet Enabled Smart Home}{IJETSR- ISSN 2394 3386}
      {Author}{Volume 4, Issue 6 | June 2017}
      \resumeItemListStart
        \resumeItem{Cost Enhancements}
          {Deviced a very cheap and efficient way of making a home smart.}
        \resumeItem{Flask, Google Speech}
          {Used Flask and HTML,CSS to create a web interface for handling the resources in home. Flask is a python based framework that can provide a stable backend to websites. Also implemeted the Google Speech API to access the voice inputs of the user.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Poliastro - OpenAstronomy}{Barcelona, Spain}
      {Software Development Intern}{May 2018 - Present}
      \resumeItemListStart
        \resumeItem{pypi release 0.10}
          {Worked for the 0.10 release of poliastro.}
        \resumeItem{Backends for Orbit Plotting}
          {Restructured the whole plotting module and created two different backends for plotting. One using plotly and the other using mat-
plotlib.}
		\resumeItem{2D Interactive Plotting}
		{Created a class for 2D plotting using plotly. This created interactive 2D plotting for orbits.}
      \resumeItemListEnd

   

    \resumeSubheading
      {Indian Institute of Technology Mandi}{Mandi, India}
      {Teaching Assistant}{Feb. 2018 - Jun. 2018}
      \resumeItemListStart
        \resumeItem{Programming and Data Structures Practicum}
          {Helped students understand complex Data Structures and Algorithms. Cleared their doubts for DS implementations in C}
      \resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{poliastro}
      {Open source python library for astrodynamics.}
    \resumeSubItem{Intelligent Fabric Detection and Classification}
      {A Deep Learning Model to identify the fabric and classify it into different classes. Data Based Training.}
    \resumeSubItem{Ayushman Bhava}
      {A smart medical vending machine with video conferencing with doctor, Payment gateway enabled for online payment. Deep Learning for Cash detection.}
    \resumeSubItem{Exoplanet Detection}
      {A Machine Learning based prediction model which predicts the presense of Exoplanets on a star by the brightness data of that star over a long period of time.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Python, C/C++, shell, NASM, Erlang, JavaScript, Dart(Flutter), MySQL}
    \resumeSubItem{Web}
      {Flask, Dash, HTML5, ,CSS3, Materialize, JavaScript, Django}
    \resumeSubItem{Markup}
      {\LaTeX, Markdown, ReStructured Text, YAML}
    \resumeSubItem{Technologies and Libraries}
      {git, mercurial, PyCharm, plotly, mayavi, Tensorflow, Keras, numba JIT}
  \resumeSubHeadingListEnd
  
%-----------PRESENTATIONS-----------------
\section{Presentations and Talks}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Astronomy Code Camp - Nehru Planetarium, Delhi}{New Delhi, India}
      {Mentor and Presenter}{Jun. 2018}
      \resumeItemListStart
        \resumeItem{Scientific Computing}
          {Introduction to various scientific computing packages such as poliastro, astropy, pyephem to the participants.}
      \resumeItemListEnd

   

    \resumeSubheading
      {6th ICETSMI-2017}{IETE, Delhi, India}
      {Presenter in 6th International Conference on Eng. Tech., Science and Mngmt. Innovation}{Jun. 2017}
      \resumeItemListStart
        \resumeItem{Paper Presentation}
          {Presented the paper titled, ”ProjectHiko1.O - The Voice and Internet Enabled Smart Home” at the conference.}
      \resumeItemListEnd



  \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
